### 2021-05-10 shared/analysis.tex
WIP : Optimization Query

for example, on the $i^{th}$ run \texttt{$\vec{d}$} can have a value.
\[
\vec{d}_{i} = encode(<0,0,0,1,1,0,1,1,1,0>)
\]

Based on the value of the $\vec{d}_{i}$, we get $w_{i}$ value using $choice\_prob$. 
\begin{equation}
	w_{i} = {(p)^{x_i} * (1-p)^{n-x_i}}
\end{equation}
where $x_i$ denotes the number of $heads$ in the $i^{th}$ randomized run and for $n$ runs. \texttt{n = 10} for the case in the above example. \\

We consider top "$k$" randomized runs now for the optimization query. The expression for \texttt{optimization} thus becomes 
\[	
	maximize(\sum_{i=1}^{k}{w_i})
\]
On substituting the value of $w_i$ from (1).
\begin{equation}	
	maximize(\sum_{i=1}^{k}{(p)^{x_i} * (1-p)^{n-x_i}})
\end{equation}

@@

\end{document}

>>>>

concretely, on the $i^{th}$ run \texttt{$\vec{d}$} can have a value as below, \texttt{one-hot} encoded $w.r.t$ the outcome of $heads$ or $tails$.
\[
\vec{d}_{i} = encode(<0,0,0,1,1,0,1,1,1,0>)
\]

Based on the value of the $\vec{d}_{i}$, we get $w_{i}$ value using $choice\_prob$. 
\begin{equation}
	w_{i} = {(p)^{x_i} * (1-p)^{n-x_i}}
\end{equation}
where $x_i$ denotes the number of $heads$ in the $i^{th}$ randomized run and for $n$ runs. \texttt{n = 10} for the case in the above example. \\
\begin{equation}
	w_{i} = {(p)^{x_i} * (1-p)^{10-x_i}}
\end{equation}
We consider top "$k$" randomized runs now for the optimization query. The expression for \texttt{optimization} thus becomes 
\[	
	maximize(\sum_{i=1}^{k}{w_i})
\]
On substituting the value of $w_i$ from (1).
\begin{equation}	
	maximize(\sum_{i=1}^{k}{(p)^{x_i} * (1-p)^{n-x_i}})
\end{equation}

@@

\section{Expression for $k$-paths}

Specify the \texttt{renaming} and \texttt{constraint} solving over the \texttt{optimization} expression. Write out this algorithm formally. \\

For $k = 5$, the five \texttt{constraint} sets and \texttt{optimization} expressions are : ...
\end{document}
